---
title: "Karolinska Institutet Theme"
subtitle: "...powered by [xaringan](https://github.com/yihui/xaringan)"
author: "Developed by Alessandro Gasparini"
date: "Last updated: `r Sys.Date()`"
output:
  xaringan::moon_reader:
    css: ["ki", "ki-fonts"]
---

```{r setup, include = FALSE}
options(htmltools.dir.version = FALSE)
```

# Hello World

Install the **xaringan** package from CRAN:

```{r eval = FALSE, tidy = FALSE}
install.packages("xaringan")
```

--

You are recommended to use the [RStudio IDE](https://www.rstudio.com/products/rstudio/), but you do not have to.

- Create a new R Markdown document from the menu `File -> New File -> R Markdown -> From Template -> Ninja Presentation`;

--

- Click the `Knit` button to compile it;

--

- or use the [RStudio Addin](https://rstudio.github.io/rstudioaddins/)<sup>1</sup> "Infinite Moon Reader".

.footnote[
[1] See [#2](https://github.com/yihui/xaringan/issues/2) if you do not see the template or addin in RStudio.
]

---

# Extra colours

The `ki` theme includes extra colours and font sizes.

Colours: .plum[`.plum[]`], .dark-plum[`.dark-plum[]`], .grey[`.grey[]`], .light-grey[`.light-grey[]`], .white[`.white[]`], .black[`.black[]`], .blackish[`.blackish[]`], .orange[`.orange[]`], .light-orange[`.light-orange[]`], .light-blue[`.light-blue[]`], .main[`.main[]`], .accent[`.accent[]`], .text[`.text[]`], .text-inverse[`.text-inverse[]`].

The colours of the theme can be easily customised - see `ki.css`.

---

# Extra font sizes:

The `ki` theme includes extra colours and font sizes.

Font-sizes: .tiny[(.)tiny[]], .scriptsize[(.)scriptsize[]], .footnotesize[(.)footnotesize[]], .small[(.)small[]], .normalsize[(.)normalsize[]], .large[(.)large[]], .Large[(.)Large[]], .LARGE[(.)LARGE[]], .huge[(.)huge[]], .Huge[(.)Huge[]], .references[(.)references[]].

---

# Lists

1. One

2. Two

3. Three


* A

* B

* C

---

# R output

```{r cars}
s <- summary(cars)
s
```

---

# Plot

```{r pressure, echo = FALSE}
plot(pressure)
```

---

# Disclaimer

The Karolinska Institutet logo is used for dissemination purposes only.

Please read the webpage with the visual identity guidelines before using this template: https://staff.ki.se/brand-platform-and-graphic-profile
