---
title: "UoL Theme"
subtitle: "...powered by xaringan"
author: "Alessandro Gasparini"
date: "Last updated: `r Sys.Date()`"
output:
  xaringan::moon_reader:
    css: ["uol", "uol-fonts"]
    lib_dir: libs
    nature:
      highlightStyle: github
      countIncrementalSlides: false
---

```{r setup, include = FALSE}
options(htmltools.dir.version = FALSE)
```

# Hello World

Install the **xaringan** package from [Github](https://github.com/yihui/xaringan):

```{r eval=FALSE, tidy=FALSE}
remotes::install_github("yihui/xaringan")
```

--

You are recommended to use the [RStudio IDE](https://www.rstudio.com/products/rstudio/), but you do not have to.

- Create a new R Markdown document from the menu `File -> New File -> R Markdown -> From Template -> Ninja Presentation`;<sup>1</sup>

--

- Click the `Knit` button to compile it;

--

- or use the [RStudio Addin](https://rstudio.github.io/rstudioaddins/)<sup>2</sup> "Infinite Moon Reader" to live preview the slides (every time you update and save the Rmd document, the slides will be automatically reloaded in RStudio Viewer.

.footnote[
[1] 中文用户请看[这份教程](https://slides.yihui.org/xaringan/zh-CN.html)

[2] See [#2](https://github.com/yihui/xaringan/issues/2) if you do not see the template or addin in RStudio.
]

---

# Extra colours

The `uol` theme includes extra colours and font sizes.

Colours: .corporate-red[`.corporate-red[]`], .corporate-grey[`.corporate-grey[]`], .white[`.white[]`], .vibrant-red[`.vibrant-red[]`], .orange[`.orange[]`], .warm-yellow[`.warm-yellow[]`], .vc-green[`.vc-green[]`], .dark-green[`.dark-green[]`], .mid-green[`.mid-green[]`], .acid-green[`.acid-green[]`], .dark-blue[`dark-blue[]`], .mid-blue[`.mid-blue[]`], .light-blue[`.light-blue[]`], .mauve-blue[`.mauve-blue[]`], .dark-warm-grey[`.dark-warm-grey[]`], .mid-warm-grey[`.mid-warm-grey[]`], .light-warm-grey[`.light-warm-grey[]`], .black[`.black[]`], .mid-cool-grey[`.mid-cool-grey[]`], .light-cool-grey[`.light-cool-grey[]`], .digi-gold[`.digi-gold[]`], .light-digi-gold[`.light-digi-gold[]`], .magenta[`.magenta[]`], .bright-yellow[`.bright-yellow[]`], .cyan[`.cyan[]`], .royal-blue[`.royal-blue[]`], .metallic-gold[`.metallic-gold[]`], .metallic-gold-70p[`.metallic-gold-70p[]`], .metallic-silver[`.metallic-silver[]`], .metallic-silver-70p[`.metallic-silver-70p[]`], .main[`.main[]`], .accent[`.accent[]`], .text[`.text[]`], .text-inverse[`.text-inverse[]`].

The colours of the theme can be easily customised - see `uol.css`.

---

# Extra font sizes:

The `uol` theme includes extra colours and font sizes.

Font-sizes: .tiny[`.tiny[]`], .scriptsize[`.scriptsize[]`], .footnotesize[`.footnotesize[]`], .small[`.small[]`], .normalsize[`.normalsize[]`], .large[`.large[]`], .Large[`.Large[]`], .LARGE[`.LARGE[]`], .huge[`.huge[]`], .Huge[`.Huge[]`], .references[`.references[]`].

---

# Lists

1. One
2. Two
3. Three

* A
* B
* C

---

# R output

```{r cars}
summary(cars)
```

---

# Plot

```{r pressure, echo = FALSE}
plot(pressure)
```

---

# Disclaimer

The university logo is used for dissemination purposes only - please read the webpage with the visual identity guidelines: https://www2.le.ac.uk/offices/external/marcomms/creative/identity

The logo is still property of the University of Leicester (https://le.ac.uk/).
